---
title: "UAW-GM Cohort Study"
# author: "Kevin Chen"
subtitle: "Clean referent group, messy exposure groups; exposure lagged 21 years"
date: \today
output:
  # word_document
  pdf_document:
    # latex_engine: lualatex
    includes:
      in_header: '~/HeadRs/StatHead.sty'
# bibliography: ./../../references/gm.bib
# csl: "C:/Users/kevchen/Documents/HeadRs/AMA.csl"
geometry: margin=2.4cm
---

\fancyhead[R]{Clean referent group, messy exposure groups; exposure lagged 21 years}
\renewcommand{\arraystretch}{1.1}
\renewcommand{\headrulewidth}{0pt}
\thispagestyle{empty}

```{r setup, include=F}
knitr::opts_chunk$set(echo = F,
											warning = F,
											message = F,
											# cache = F,
											fig.align = 'center',
											fig.pos = 'H',
											results = 'asis')

library(here)
library(pander)
library(knitr)
library(tidyverse)
library(data.table)
library(date)
library(Hmisc)

source(here::here('wrangling', '00-my-theme.R'))
drive_D <- T

# table.engine <- "pander"
table.engine <- "xtable"
upper.percentile <- 0.99
messyref <- NULL

```

```{r, results='hide', echo=F, warning=F, message=F}
# rm(list = ls())
# rm(cohort_analytic, exposure.lag)
outcome.selected <- c("Laryngeal cancer",	"Lung cancer",
											"Esophageal cancer", "Stomach cancer",
											"Colon cancer",
											"Rectal cancer", "Bladder cancer",
											"Liver cancer",
											"Pancreatic cancer", "Skin cancer",
											"Prostate cancer", "Brain and nervous system cancers",
											"Leukemia", "Breast cancer"
											)

if (!('cohort_analytic' %in% ls())) {
	outcome.type <- 'mortality'
	exposure.lag <- 21
	# source(here::here('modeling', 'modeling.R'))
}

```

## Introduction

In previous survival analyses, hazard ratios associated with exposure to the three metalworking fluid types were estimated simultaneously in the same Cox proportional hazards model. There was a concern that those estimates may have been biased or misleading, as those models assumed independent covariate (statistical) effects e.g. that the effect of exposure to straight metalworking fluids was constant across levels of exposure to other metalworking fluid types. One way we attempted to address this concern was to fit independent models for each exposure-outcome pair of interest where person-time included in the analytic dataset would be restricted to those where either (1) cumulative exposure was zero or (2) cumulative exposure to the exposure of interest was nonzero. In other words, we excluded person-time satisfying both (1) zero exposure to the metalworking fluid type of interest _and_ (2) nonzero exposure to some metalworking fluid other than the type in which we were interested. Coding of exposure and potential confounders was equivalent as that in the original analyses. As in the previous analyses, the category cut-points for the continuous covariates were determined in a data-adaptive way, so covariate definitions may vary from model to model. The results from the $13 \times 3 = 39$ models are presented below.

## Results

```{r table, eval=F}
# Column widths in inches should be
# 1.5   0.94   1.2   0.42   0.42   1   0.22
source(here::here('reports', 'coef.R'))

get.ctab(
	outcome_selected = outcome.selected,
	coxph.dir  = paste0('modeling/resources/mortality/emm/lag ', exposure.lag, '/clean_referent/'),
	output.dir = paste0('reports/emm/resources/lag ', exposure.lag, '/clean_referent'),
	mwf.vec = c("Straight", "Soluble", "Synthetic"),
	messy_ref = NULL,
	clean_referent = T
	)

get.ctab(
	outcome_selected = outcome.selected,
	coxph.dir  = paste0('modeling/resources/mortality/emm/lag ', exposure.lag, '/clean_referent/'),
	output.dir = paste0('reports/emm/resources/lag ', exposure.lag, '/clean_referent'),
	mwf.vec = c("Straight", "Soluble", "Synthetic"),
	messy_ref = '_sol500',
	clean_referent = T
	)

get.ctab(
	outcome_selected = outcome.selected,
	coxph.dir  = paste0('modeling/resources/mortality/emm/lag ', exposure.lag, '/clean_referent/'),
	output.dir = paste0('reports/emm/resources/lag ', exposure.lag, '/clean_referent'),
	mwf.vec = c("Straight", "Soluble", "Synthetic"),
	messy_ref = '_sol10',
	clean_referent = T
	)

get.ctab(
	outcome_selected = outcome.selected,
	coxph.dir  = paste0('modeling/resources/mortality/emm/lag ', exposure.lag, '/clean_referent/'),
	output.dir = paste0('reports/emm/resources/lag ', exposure.lag, '/clean_referent'),
	mwf.vec = c("Straight", "Soluble", "Synthetic"),
	messy_ref = '_sol5',
	clean_referent = T
	)

```

```{r table.render}
# messyref <- NULL
# messyref <- '_sol500'
# messyref <- '_sol10'
# messyref <- '_sol5'

load(to_drive_D(here::here(
	paste0('reports/emm/resources/lag ', exposure.lag, '/clean_referent'),
	paste0(substring(messyref, 2), ifelse(!is.null(messyref), '.', ''), 'coxph.tab.rdata'))))

names(coxph.tab)[1:2] <- c(' ', '  ')

source(here::here('reports', 'coef.R'))

for(mwf in c("Straight", "Soluble", "Synthetic")) {
	render.ctab(mwf_which = mwf)
}

```

```{r tikz, eval=F}
coxph.ggtab <- as.data.table(as.data.frame(coxph.tab[!is.na(`  `), .(
	Outcome = factor(outcome, levels = unique(outcome)),
	exposure = factor(gsub("\\\\\\hspace\\{.*\\}|&#9;", "", `  `),
										levels = unique(
											gsub("\\\\\\hspace\\{.*\\}|&#9;", "", `  `)
										)),
	HR = as.numeric(HR),
	lower = as.numeric(substr(`95\\% CI`, 2, unlist(
		gregexpr(',', `95\\% CI`)
	) - 1)),
	upper = as.numeric(substr(
		`95\\% CI`, unlist(gregexpr(',', `95\\% CI`)) + 2,
		nchar(`95\\% CI`) - 1
	)),
	`$p$`,
	mwf
)]))

# Prep for Straight
coxph.ggtab[exposure != 'Trend' & mwf == "Straight"] %>%
	as.data.frame() %>%	as.data.table() -> Straight.ggtab
Straight.ggtab[, I := 1:.N]
Straight.ggtab <- Straight.ggtab[exposure != '0']
# Prep for Soluble
coxph.ggtab[exposure != 'Trend' & mwf == "Soluble"] %>%
	as.data.frame() %>%	as.data.table() -> Soluble.ggtab
Soluble.ggtab[, I := 1:.N]
Soluble.ggtab <- Soluble.ggtab[exposure != '0']
# Prep for Synthetic
coxph.ggtab[exposure != 'Trend' & mwf == "Synthetic"] %>%
	as.data.frame() %>%	as.data.table() -> Synthetic.ggtab
Synthetic.ggtab[, I := 1:.N]
Synthetic.ggtab <- Synthetic.ggtab[exposure != '0']

tikz(here::here(
	paste0('reports/emm/resources/lag ', exposure.lag, '/clean_referent'),
	paste0('hr_plot',  messyref, '.tex')),
	standAlone = T, width = 6.5, height = 9)
cowplot::plot_grid(
	# Plot Straight
	Straight.ggtab %>% ggplot(aes(
		x = I,
		y = HR,
		ymin = lower,
		ymax = upper,
		shape = Outcome
	), ) +
		geom_pointrange(size = 0.07) +
		scale_shape_manual(values = c(1:7, 1:7)) +
		# geom_linerange() +
		facet_wrap(. ~ mwf, scales = 'free_x', ncol = 1) +
		scale_x_continuous(breaks = Straight.ggtab[,.(I[-1]), by = .(Outcome)]$V1,
											 labels = Straight.ggtab[,.(exposure[-1]), by = .(Outcome)]$V1) +
		coord_cartesian(ylim = c(0, 4)) +
		geom_hline(aes(yintercept = 1), color = 'gray') +
		mytheme +
		theme(
			panel.grid = element_blank(),
			axis.text.x = element_text(angle = -90, vjust = 0.35, hjust = 0),
			axis.title.x = element_blank()
		) +
		# Suppress legend
		theme(legend.position = 'none')
	,
	# # Blank
	# ggplot(data.frame()) + geom_pointrange(size = 0.07) + theme_void()
	# ,
	# Plot soluble
	Soluble.ggtab %>% ggplot(aes(
		x = I,
		y = HR,
		ymin = lower,
		ymax = upper,
		shape = Outcome
	),) +
		geom_pointrange(size = 0.07) +
		scale_shape_manual(values = c(1:7, 1:7)) +
		# geom_linerange() +
		facet_wrap(. ~ mwf, scales = 'free_x', ncol = 1) +
		scale_x_continuous(breaks = Soluble.ggtab[,.(I[-1]), by = .(Outcome)]$V1,
											 labels = Soluble.ggtab[,.(exposure[-1]), by = .(Outcome)]$V1) +
		coord_cartesian(ylim = c(0, 4)) +
		geom_hline(aes(yintercept = 1), color = 'gray') +
		mytheme +
		theme(
			panel.grid = element_blank(),
			axis.text.x = element_text(angle = -90, vjust = 0.35, hjust = 0),
			axis.title.x = element_blank()
		) +
		# Suppress legend
		theme(legend.position = 'none')
	,
	# Plot synthetic
	Synthetic.ggtab %>% ggplot(aes(
		x = I,
		y = HR,
		ymin = lower,
		ymax = upper,
		shape = Outcome
	),) +
		geom_pointrange(size = 0.07) +
		scale_shape_manual(values = c(1:7, 1:7)) +
		# geom_linerange() +
		facet_wrap(. ~ mwf, scales = 'free_x', ncol = 1) +
		scale_x_continuous(breaks = Synthetic.ggtab[,.(I[-1]), by = .(Outcome)]$V1,
											 labels = Synthetic.ggtab[,.(exposure[-1]), by = .(Outcome)]$V1) +
		coord_cartesian(ylim = c(0, 4)) +
		geom_hline(aes(yintercept = 1), color = 'gray') +
		mytheme +
		theme(
			panel.grid = element_blank(),
			axis.text.x = element_text(angle = -90, vjust = 0.35, hjust = 0),
			axis.title.x = element_blank()
		) +
		# Suppress legend
		theme(legend.position = 'none')
	,
	# # Blank
	# ggplot(data.frame()) + geom_pointrange(size = 0.07) + theme_void()
	# ,
		# Legend
	get_legend(
		Soluble.ggtab %>% ggplot(aes(
			x = I,
			y = HR,
			ymin = lower,
			ymax = upper,
			shape = Outcome
		)) + geom_pointrange() + mytheme + 
			theme(legend.position = 'bottom') +
			scale_shape_manual(values = c(1:7, 1:7)) +
			guides(shape = guide_legend(override.aes = list(size = 0.06),
																	ncol = 4,
																	byrow = T))
	)
	,
	nrow = 4,
	ncol = 1,
	rel_heights = c(1, 1, 1, 0.5)
)
dev.off()

```

```{r tikz.render}
knitr::include_graphics(here::here(
	paste0('reports/emm/resources/lag ', exposure.lag, '/clean_referent'),
	paste0('hr_plot',  messyref, '.pdf')))

```