---
title: "UAW-GM Cohort Study"
# author: "Kevin Chen"
# subtitle: "Exposure lagged 21 years"
date: \today
output:
  # word_document
  pdf_document:
    latex_engine: lualatex
    includes:
      in_header: '~/HeadRs/StatHead.sty'
classoption: landscape
# bibliography: ./../../references/gm.bib
# csl: "C:/Users/kevchen/Documents/HeadRs/AMA.csl"
geometry: margin=2.4cm
---

\thispagestyle{empty}
\fancyhead[R]{Tabulation by exposurehistory}
\renewcommand{\arraystretch}{1.1}
\renewcommand{\headrulewidth}{0pt}

```{r setup, include=F}
knitr::opts_chunk$set(echo = F,
											warning = F,
											message = F,
											# cache = F,
											fig.align = 'center',
											fig.pos = 'H',
											results = 'asis',
											eval = F)

library(here)
library(pander)
library(knitr)
library(tidyverse)
library(data.table)
library(date)
library(Hmisc)

library(here)
library(survival)

```


```{r, results='hide', echo=F, warning=F, message=F}
source(here::here('wrangling', '00-my-theme.R'))

if (!('outcome.type' %in% ls())) {
	outcome.type <- 'mortality'
}

if (!('probs' %in% ls())) {
	probs <- seq(0, 1, 1/3)
}

if (!('exposure.lag' %in% ls())) {
	exposure.lag <- 21
	}

# Get outcome/exposure data ####
if (!('cohort_analytic' %in% ls())) {
	source(here::here('wrangling', '05-Get-Exposure-Outcome.R'))
	cohort_analytic <- get.cohort_analytic(
		outcome_type = outcome.type,
		exposure.lag = exposure.lag,
		deathage.max = NULL
		)
	setorder(cohort_analytic, studyno, year)
	cohort_analytic <- cohort_analytic[year >= 1941 & (
		year(yin) < 1938 | year >= year(yin + 365.25 * 3)
		) & yout - yin > 3]
}

outcome.selected <- c("Laryngeal cancer",	"Lung cancer",
											"Esophageal cancer", "Stomach cancer",
											"Colon cancer",
											"Rectal cancer", "Bladder cancer",
											"Liver cancer",
											"Pancreatic cancer", "Skin cancer",
											"Prostate cancer", "Brain and nervous system cancers",
											"Leukemia"
											)

```

```{r}
as.data.frame(t(sapply(outcome.selected, function(outcome) {
	cohort_analytic[
	wh == 1 & nohist == 0 & right.censored == 0 & immortal == 0 &
	get(outcome) == 1, .(
	Outcome = paste(outcome),
	`Total` = length(studyno),
	None = length(studyno[cum_straight == 0 & cum_soluble == 0 & cum_synthetic == 0]),
	`No straight` = length(studyno[cum_straight == 0 & (cum_soluble > 0 | cum_synthetic > 0)]),
	`No soluble` = length(studyno[cum_soluble == 0 & (cum_straight > 0 | cum_synthetic > 0)]),
	`No synthetic` = length(studyno[cum_synthetic == 0 & (cum_soluble > 0 | cum_straight > 0)]),
	`Only straight` = length(studyno[(cum_soluble == 0 & cum_synthetic == 0 & cum_straight > 0)]),
	`Only soluble` = length(studyno[(cum_straight == 0 & cum_synthetic == 0 & cum_soluble > 0)]),
	`Only synthetic` = length(studyno[(cum_straight == 0 & cum_soluble == 0 & cum_synthetic > 0)])
	)
]
}))) -> cases.tab

cases.tab[,-1] %>% apply(2, function(x) as.numeric(unlist(x))) -> cases.tab[,-1]

cases.tab$Outcome %>% unlist -> cases.tab$Outcome

cases.tab <- as.data.frame(rbind(cases.tab,
			cohort_analytic[
		wh == 1 & nohist == 0 & right.censored == 0 & immortal == 0, .(
			cum_straight = cum_straight[.N],
			cum_soluble = cum_soluble[.N],
			cum_synthetic = cum_synthetic[.N]
		), by = .(studyno)][,.(
	Outcome = 'All individuals at end of follow-up',
	`Total` = length(studyno),
	None = length(studyno[cum_straight == 0 & cum_soluble == 0 & cum_synthetic == 0]),
	`No straight` = length(studyno[cum_straight == 0 & (cum_soluble > 0 | cum_synthetic > 0)]),
	`No soluble` = length(studyno[cum_soluble == 0 & (cum_straight > 0 | cum_synthetic > 0)]),
	`No synthetic` = length(studyno[cum_synthetic == 0 & (cum_soluble > 0 | cum_straight > 0)]),
	`Only straight` = length(studyno[(cum_soluble == 0 & cum_synthetic == 0 & cum_straight > 0)]),
	`Only soluble` = length(studyno[(cum_straight == 0 & cum_synthetic == 0 & cum_soluble > 0)]),
	`Only synthetic` = length(studyno[(cum_straight == 0 & cum_soluble == 0 & cum_synthetic > 0)])
	)
]))

rownames(cases.tab) <- cases.tab$Outcome

cases.tab <- cases.tab[,-1]

cases.tab %>% xtable(
		caption =  paste0(
			"Number of cases by cumulative exposure at time of death."
		),
		digits = 0,
		align = "lrrrrrrrr"
	) %>% print.xtable(
		include.rownames = T,
		hline.after = c(-1, nrow(.) - 1, nrow(.)),
		tabular.environment = 'longtable',
		floating = F,
		add.to.row = list(pos = list(0),
											command = c(
												paste(
													'\\hline \n',
													'\\endhead \n',
													'\\hline \n',
													'\\endfoot \n',
													'\\endlastfoot \n'
												)
											)))


```

\begin{longtable}{lrrrrrrrr}
\caption{Number of cases by cumulative exposure at time of death.} \\ 
  \toprule
 & Total & None & No straight & No soluble & No synthetic & Only straight & Only soluble & Only synthetic \\ 
  \hline 
 \endhead 
 \hline 
 \endfoot 
 \endlastfoot 
Laryngeal cancer & 74 & 18 & 23 & 1 & 37 & 0 & 22 & 0 \\ 
  Lung cancer & 1894 & 374 & 593 & 39 & 1003 & 31 & 532 & 5 \\ 
  Esophageal cancer & 184 & 35 & 52 & 2 & 98 & 2 & 47 & 0 \\ 
  Stomach cancer & 194 & 54 & 50 & 4 & 96 & 3 & 45 & 0 \\ 
  Colon cancer & 407 & 65 & 146 & 7 & 245 & 5 & 135 & 1 \\ 
  Rectal cancer & 89 & 18 & 27 & 0 & 44 & 0 & 23 & 0 \\ 
  Bladder cancer & 143 & 25 & 49 & 2 & 82 & 2 & 41 & 0 \\ 
  Liver cancer & 128 & 17 & 41 & 3 & 76 & 3 & 39 & 0 \\ 
  Pancreatic cancer & 315 & 62 & 92 & 5 & 165 & 4 & 86 & 1 \\ 
  Skin cancer & 73 & 14 & 21 & 2 & 41 & 2 & 19 & 0 \\ 
  Prostate cancer & 418 & 57 & 135 & 8 & 244 & 7 & 123 & 0 \\ 
  Brain and nervous system cancers & 128 & 29 & 45 & 2 & 65 & 2 & 40 & 0 \\ 
  Leukemia & 200 & 40 & 60 & 5 & 102 & 3 & 52 & 2 \\ 
   \midrule
All individuals at end of follow-up & 38640 & 6105 & 12180 & 703 & 20023 & 540 & 10345 & 114 \\ 
   \bottomrule
\end{longtable}